Species motif participation provides unique information about species risk of extinction

### 2023-04-20 manuscript/reorder_main_text.tex

        The removal of cycles also affects which motifs can appear in the network. 
        Any motif which contains a cycle is impossible in an acyclic network.
        This means that only the four motifs which are most common in empirical networks (\citealp[]{Stouffer2007}: apparent competition, direct competition, omnivory, and the three-species chain) can appear.
        Fortunately, they are also the motifs that have been most studied in isolation (e.g.,~\citep{}) and have the clearest ecological interpretation and, as such, are of greatest interest to us.

>>>>

        The removal of cycles also affects which motifs can appear in the network. 
        Any motif which contains a cycle is impossible in an acyclic network.
        This means that only the four motifs which are most common in empirical networks (\citealp[]{Stouffer2007}: apparent competition, direct competition, omnivory, and the three-species chain) can appear.
        Fortunately, they are also the motifs that have been most studied in isolation (e.g.,~\citep{Hastings1991,Holt1987,Bascompte2005,Polis1989,Zabalo2012,Lefevre2009,Holt1997,Kondoh2008,McKinnon2013,Laws2013}) and have the clearest ecological interpretation and, as such, are of greatest interest to us.
